Investigating the Underprovision of Public Goods: Does Segregation Matter?

### 2020-05-09 Burzillo_Trounstine_Replication.Rmd
final draft commit

kable(imp_felm1_sum_table_vars, 
      "latex",
      caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for all Cities}",
      align = c("l","c","c","c"),
      booktabs = T) %>%
    row_spec(0, bold = TRUE) %>%
  footnote(symbol = c("N = 73,119"),
    general = c("This table shows the results of Trounstine's first model for the effect of segregation on per capita direct",
  "public expenditure using the two-group Theil's H Segregation Index and the new, multiply imputed datasets.",
  "The results present a stark contrast to Trounstine's original results: the main coefficient on segregation index",
  "has decreased to essentially zero and has become statistically insignificant.  The coefficient on diversity has",
  "increased in magnitude and become statistically significant."),
  footnote_order = c("symbol", "general"),
           general_title = "Table 4:") %>%
  kable_styling(full_width = TRUE, latex_options = "hold_position")

@@

![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016. My replication of these results can be found in Table 5 in the Appendix of this paper.](table_1.png)

>>>>

kable(imp_felm1_sum_table_vars, 
      "latex",
      caption = "\\textbf{Effect of Segregation on Overall per Capita Direct General City Expenditures: Imputed Data for all Cities}",
      align = c("l","c","c","c"),
      booktabs = T) %>%
    row_spec(0, bold = TRUE) %>%
  footnote(symbol = c("N = 73,119"),
    general = c("This table shows the results of Trounstine's first model for the effect of segregation on per capita direct",
  "public expenditure using the two-group Theil's H Segregation Index and the new, multiply imputed datasets.",
  "The results present a stark contrast to Trounstine's original results: the main coefficient on segregation index",
  "has decreased to essentially zero and has become statistically insignificant.  The coefficient on diversity has",
  "increased in magnitude and become statistically significant."),
  footnote_order = c("symbol", "general"),
           general_title = "Table 2:") %>%
  kable_styling(full_width = TRUE, latex_options = "hold_position")

@@

### Figure 7
![This is the original table displaying the results of the models for the effects of residential segregation on political polarization from page 713 of @trounstine_segregation_2016. My replication of these results can be found in Table 5 in the Appendix of this paper.](table_1.png)
